I would like to express my sincere gratitude to my advisor and mentor, Dr. Ayan Mukhopadhyay\footnotemark{} for the continuous support throughout my undergraduate study at IIT Madras. Since my first academic day, when I first met him, his encouragement and guidance and challenging me with hard physics problems have greatly impacted my current research abilities. He has constantly helped me with the writing of this thesis and the work it presents.
\footnotetext{Associate Professor, Department of Physics, Indian Institute of Technology Madras}

I would also like to thank my co-advisor, Dr. Vishnu Jejjala\footnotemark{}, for his invaluable insights during weekly discussions and his constant support during the writing of this thesis.
\footnotetext{Professor, School of Physics, University of the Witwatersrand}

Besides the advisors for this thesis, I would like to thank Dr. Boris Pioline\footnotemark{} for offering me the opportunity to work under his supervision in a summer internship in Paris on a related subject, Shivaprasad Hulyal (Engineering Physics major, IIT Madras) for his help with some of the simulations presented in this thesis, and Tanay Kibe (Doctoral Candidate, IIT Madras) for helpful discussions on the subject.
\footnotetext{Senior, Le Laboratoire de Physique Théorique et Hautes Énergies (LPTHE), Paris}

Lastly, this work would not have been successful without the constant and continuing support of my close friend, Ananya Shetty, and my parents, Ashok Kumar and Poonam.